Exploring inductive bias to assess music structure analysis (MSA) \\ \large An audio-based approach using musically motivated deep learning to gain insight into the underlying structure of music

### 2023-02-18 introduction/introduction.tex
Updates from Overleaf

Music is a complex and fascinating art form that has been studied by scholars and musicians for centuries. Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.

Recently, the field of Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music. This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.

@@

The goal of this research is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.

>>>>

Music is a complex and fascinating art form studied by scholars and musicians for centuries. Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.

Recently, Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music. This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.

In recent years, the utilization of neural networks has allowed for the creation of low-dimensional musical embeddings that capture important musical features and enable the computation of semantic similarity between musical passages. By learning an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can quantify the semantic similarity between two musical passages using the Euclidean distance, which is represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$. Adequate embedding space is essential in ensuring that the generated output aligns with human expectations, especially in interactive applications where a human performer influences the machine's response. The success of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.

@@

This research aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
